Bayesian model in JAGS

### 2023-01-17 JAGS_Bayesian_model/Jags_Bayesian_model.Rmd
add basic timing model

## Corresponding model structure without considering spatial autocorrelation

```{r}
Nospatial_model <- "model{
for(i in 1:n){
Z[i] ~ dnorm(mu[i], inv_var)
 mu[i] <- (beta0+x1[i]*lambda1+x2[i]*lambda2+lambda3*x3[i])+(beta1+x1[i]*theta1+x2[i]*theta2+theta3*x3[i])*log_W[i]
}

beta0~dnorm(0,0.0001)
beta1~dnorm(0,0.0001)
lambda1~dnorm(0,0.0001)
lambda2~dnorm(0,0.0001)
lambda3~dnorm(0,0.0001)
theta2~dnorm(0,0.0001)
theta1~dnorm(0,0.0001)
theta3~dnorm(0,0.0001)

inv_var ~ dgamma(0.01, 0.01)
}
"
```

>>>>

## Jags model code without considering spatial autocorrelation

```{r}
Nospatial_model <- "model{
################ model ####################################
for(i in 1:n){
Y[i] ~ dnorm(mu[i], inv_var)
 mu[i] <- alpha_0[i] + beta1*log_Z[i]
 # log_Z is the log transform average relative timing of RSV

alpha_0[i]= beta0+x1[i]*lambda1+x2[i]*lambda2+lambda3*x3[i]
# this is alpha_0i = beta0 + X_i*lambda (coviariates)
}

################ priors ####################################
beta0~dnorm(0,0.0001)
beta1~dnorm(0,0.0001)
lambda1~dnorm(0,0.0001)
lambda2~dnorm(0,0.0001)
lambda3~dnorm(0,0.0001)

inv_var ~ dgamma(0.01, 0.01)}"
```

## Load the data and run the jags model to sample posteriors

```{r,eval=FALSE}
## loading data from the working directory
data <- readRDS("./Nospatial_model.rds")

### Read in the model file using the jags.model function ##
non_spatial <- jags.model(textConnection(Nospatial_model),
                     data=data,n.chains = 4)

############ burn-in period ############
update(non_spatial,10000)

######## sample for posterior distribution ##########
non_spatial_sample <- coda.samples(non_spatial,c("beta0","beta1",
                            "lambda1","lambda2",
                            "lambda3","inv_var"),
                             100000,thin=20)
```

## Summarize the posterior distribution

```{r,eval=FALSE}
summary(non_spatial_sample)
```

## Check for model convergence (gelman diagnostic)

```{r,eval=FALSE}
gelman.diag(non_spatial_sample)
```

## Trace plots

```{r,eval=FALSE}
par(mfrow=c(3,2))
traceplot(non_spatial_sample)
```

## Density plot of the posterior distributions

```{r,eval=FALSE}
par(mfrow=c(3,2))
densplot(non_spatial_sample)
```
